Dynamic Knapsack Problem

### 2021-04-09 Manuscript/Manuscript.tex
trying to find the bugs
updates go brrrr

\subsection{Questions}
\begin{itemize}
	\item Need to change generating an action section (4.7)
	\item Priority need to be added
	\item PPE resources need to include OR time
	\item Add cost of scheduling past the window
	\item Evaluate cost of waiting
\end{itemize}

@@

\subsection{State Space}
\subsubsection{Description}
State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{pe}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
    \item $\vec{pe} = pe_{dc}$ - Number of patients of complexity $d$, CPU $c$ expected to arrive this period
    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
\end{itemize}
\subsubsection{Bounds on States}
\begin{itemize}
	\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
	\item $uu_{tp} \le 2(uen_{p} + max(ued_p)) \quad \forall tp$
	\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
	\item $pe_{dc} \le pea_{dc} * 4 \quad \forall dc$
	\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
	\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
\end{itemize}

@@

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Total number of PPE units cannot be exceeded  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			( \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp
		\end{equation}

>>>>

\subsection{Questions}
\begin{itemize}
	\item Need to change generating an action section (4.7)
	\item Priority need to be added
	\item PPE resources need to include OR time
	\item When generating a new state for master (section 4.5), do I need to ensure the states are consistent, etc?
\end{itemize}

@@

\subsection{State Space}
\subsubsection{Description}
State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{pe}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
    \item $\vec{pe} = pe_{dc}$ - Number of patients of complexity $d$, CPU $c$ expected to arrive this period
    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
\end{itemize}
\subsubsection{States Constraints}
\begin{itemize}
	\item PPE Usage Constraint
	\begin{equation}
		uu_{tp} = ue_{tp}+uv_{tp} \quad \forall tp
	\end{equation}
	\item Bounds on states
	\begin{itemize}
		\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uu_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $pe_{dc} \le pea_{dc} * 4 \quad \forall dc$
		\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
		\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
	\end{itemize}
\end{itemize}

@@

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Tracks PPE Usage  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			(\sum_{mdc}ps_{tmdc} \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
		\end{equation}
